Pattern matching for\\ $(231,213)$-avoiding permutations

### 2015-02-02 article.tex
modification : environement proof used. modification : proof change if both permutation avoid 231,213.

\begin{corollary}
$\pi \in \AV_n(213,231)$ if and only if for $1 \leq i \leq n$, 
$\pi[i:]$ start either with the maximal element
or the minimal element of $\pi[i:]$.
\end{corollary}

@@

We need the following lemmata.

\begin{lemma}
\label{lemma:updown}
Let $\pi \in \AV_n(213,231)$.
For all $1 \leq i < j \leq n$, 
if $\stripe{\pi}{i}=\ustep$
and $\stripe{\pi}{j}=\dstep$
then $\pi(i)<\pi(j)$.
\end{lemma}

\begin{proof} 
By induction on the size of the permutation.
The proposition is certainly true for the $12$ and $21$.
Suppose the proposition holds true for $\AV_n(213,231)$.
Let $\pi \in \AV_{n+1}(213,231)$ and
$\pi'$ be the permutation $\pi[2:]$.
$\pi' \in \AV_n(213,231)$.
By induction hypothesis, we only need to compare the first
element of $\pi'$ to every element in $\pi'$.
According to lemma~\ref{lemma:first element is 1 or n},
the first element of $\pi$ is either $1$ or $n$.
If the first element of $\pi$ is $1$ then $s_\pi(1) = a$
and $\pi(i) < \pi(j)$ for every $2 \leq j \leq n$.
If the first element of $\pi$ is $n$ then
 $s_\pi(1) = d$.
\qed
\end{proof}

		\begin{lemma}
		\label{lemma:upup}
		Let $\pi \in \AV_n(213,231)$,
		$\forall i,j \in [n]$, 
		$i<j$, 
		if $\stripe{\pi}{i}=\ustep$
		and $\stripe{\pi}{j}=\ustep$
		then $\pi(i)<\pi(j)$.
		\end{lemma}

		In other word, for every index $i$ and $j$ of an (231,213) avoiding permutation $\pi$,
		if $i$ is a ascent
		and $j$ is a ascent
		and $ i<j$
		then $p(i)<p(j)$.\\

		%\textbf{Proof} Same as before.\\

%		\textbf{Proof} By induction on the size of the permutation :
%		the proposition is true for the permutations $(1,2)$ and $(2,1)$.
%		Suppose the proposition true for $\C{n}$.
%		Let $p \in \C{n+1}$, 
%		we show that the proposition holds for $p$.
%		Let $p'$ be the permutation $p[2:]$.
%		$p' \in \C{n}$, so
%		every element of $p'$ verify our lemma (by induction).
%		We still need to compare the first element with the rest.
%		Except that the first element
%		is the maximal (minimal) element of all the permutation 
%		(by Corollary \ref{stripe}).
%		Moreover if the first element is the maximal (minimal)
%		it will mapped to an descent (\pi_2).
%		So the proposition is also true
%		for the first element.
%		$\Box$\\

		\begin{lemma}
		\label{lemma:downdown}
 		Let $\pi \in \AV_n(213,231)$,
		$\forall i,j \in [n]$,
		$i<j$,
		if $\stripe{\pi}{i}=\dstep$
		and $\stripe{\pi}{j}=\dstep$
		then $\pi(i)>\pi(j)$.
		\end{lemma}

		In other word, for every index $i$ and $j$ of an (231,213) avoiding permutation $\pi$,
		if $i$ is a descent
		and $j$ is a descent
		and $ i<j$
		then $\pi(i)>\pi(j)$.\\

		%\textbf{Proof} Same as before.\\

%		\textbf{Proof} By induction on the size of the permutation :
%		the proposition is true for the permutations $(1,2)$ and $(2,1)$.
%		Suppose the proposition true for $\C{n}$.
%		Let $p \in \C{n+1}$, 
%		we show that the proposition holds for $p$.
%		Let $p'$ be the permutation $p[2:]$.
%		$p' \in \C{n}$, so
%		every element of $p'$ verify our lemma (by induction).
%		We still need to compare the first element with the rest.
%		Except that the first element
%		is the maximal (minimal) element of all the permutation 
%		(by Corollary \ref{stripe}).
%		Moreover if the first element is the maximal (minimal)
%		it will mapped to an descent (ascent).
%		So the proposition is also true
%		for the first element.
%		$\Box$\\

		\begin{proposition}
		\label{proposition:patternMatchingStripe}
		Let $\ptext, \pmotif \in \AV_n(213,231)$.
		$\pmotif$ is a motif of $\ptext$ if and only if the stripe of $\pmotif$ is a motif of the stripe of $\ptext$.
		\end{proposition}

		\textbf{Proof} \\
		$\Rightarrow$ Suppose that $\pmotif$ is a motif of $\ptext$
		by subsequence $s$.
		By definition $s$ normalized is equal to
		$\pmotif$ so they have the same stripe.\\ 
		$\Leftarrow$ 
		Let $\ptext$ be a permutation avoiding $(213,231)$, 
		$S_1$ be its stripe, 
		$\pmotif$  be a permutation avoiding $(213,231)$, 
		and $S_2$ its stripe.
		Let $\phi$ be the function
		that match $S_2$ to $S_1$.
		We define $\varphi$ as, 
		$\forall x \in [|\pmotif|-1]$,
		$\varphi(x) = \phi(x)$,
		and $\varphi(|\pmotif|) = \phi(|\pmotif|-1)+1$
		Suppose that $\exists x,y \in [|\pmotif|]$, 
		$\pmotif(x)<\pmotif(y)$ 
		and $\ptext(\varphi(x))>\ptext(\varphi(y))$,
		without lost of generality we can suppose that $x<y$,
		Let see all the case possible that can make this 
		hypothesis possible :
		\begin{itemize}		
			\item if $\pmotif(x)<\pmotif(y)$, 
			$\stripe{\pmotif}{x}=\ustep$ 
			and $\stripe{\pmotif}{y}=\ustep$
			(if x and y are increasing in $\pmotif$),
			then $\stripe{\ptext}{\varphi(x)} =\ustep$ and $\stripe{\ptext}{\varphi(y)}=\ustep$,
			(the match are also increasing).
			As $x<y$ and as $\varphi$ is an increasing function, 
			$\varphi(x) < \varphi(y)$.
			And thus, by \textbf{Lemma \ref{lemma:upup}},
			$\ptext(\varphi(x)) < \ptext(\varphi(y))$ .
			Which contradict our hypothesis,
			so this case is not possible.

			\item if $\pmotif(x)<\pmotif(y)$, 
			$\stripe{\pmotif}{x}=\ustep$ 
			and $\stripe{\pmotif}{y}=\dstep$
			then $\stripe{\ptext}{\varphi(x)}=\ustep$ and $\stripe{\ptext}{\varphi(y)}=\dstep$,
			As $x<y$ and as $\varphi$ is an increasing function, 
			$\varphi(x) < \varphi(y)$.
			And thus, by \textbf{Lemma \ref{lemma:updown}},
			$\ptext(\varphi(x)) < \ptext(\varphi(y))$ .
			Which contradict our hypothesis,
			so this case is not possible.

			\item if $\pmotif(x)>\pmotif(y)$, 
			$\stripe{\pmotif}{x}=\dstep$ 
			and $\stripe{\pmotif}{y}=\dstep$
			then $\stripe{\ptext}{\varphi(x)}=\dstep$ and $\stripe{\ptext}{\varphi(y)}=\dstep$,
			As $x<y$ and as $\varphi$ is an increasing function, 
			$\varphi(y) < \varphi(x)$.
			And thus, by \textbf{Lemma \ref{lemma:downdown}},
			$\ptext(\varphi(y)) > \ptext(\varphi(x))$ .
			Which contradict our hypothesis,
			so this case is not possible.

			\item if $\pmotif(x)>\pmotif(y)$, 
			$\stripe{\pmotif}{x}=\dstep$ 
			and $\stripe{\pmotif}{y}=\ustep$
			then $\stripe{\ptext}{\varphi(x)}=\dstep$ and $\stripe{\ptext}{\varphi(y)}=\ustep$,
			As $x<y$ and as $\varphi$ is an increasing function, 
			$\varphi(y) < \varphi(x)$.
			And thus, by \textbf{Lemma \ref{lemma:updown}},
			$\ptext(\varphi(y)) > \ptext(\varphi(x))$ .
			Which contradict our hypothesis,
			so this case is not possible.$\Box$

			\item If $y = |\pmotif|$ and $x=|\pmotif|-1$,
			Clearly if $\stripe{\pmotif}{x}=\ustep$,
			then $\pmotif(y)-\pmotif(x)>0$ 
			and because we have a match in the ribbon
			$\ptext(\varphi(y))-\ptext(\varphi(x))>0$.
			Same idea goes if $\stripe{\pmotif}{x}=\dstep$.
			So this case is not possible.

			\item if $y = |\pmotif|$ and $x<|\pmotif|-1$,
			if $\stripe{\pmotif}{x}=\ustep$ ie
			$\pmotif(x+1)-\pmotif(x)>0$. Then
			we must have either
			$\pmotif(x)<\pmotif(x+1)<\pmotif(|\pmotif|)$
			or $\pmotif(x)<\pmotif(|\pmotif|)<\pmotif(x+1)$ 
			to avoid $231$ or $213$ in the motif.
			Because we have a match in the stripe
			and what we prove above,
			$\ptext(\varphi(x+1)-\ptext(\varphi(x))>0$.
			But by hypothesis $\ptext(\varphi(|\ptext|))<\ptext(\varphi(x))$,
			so we have either 		
			$\pmotif(|\pmotif|)<\pmotif(x)<\pmotif(x+1)$
			or $\pmotif(|\pmotif|)<\pmotif(x)<\pmotif(x+1)$ 
			which both lead to a $231$ or a $213$ motif
			in the text which is not possible.
			The same idea goes if $\stripe{\pmotif}{x}=\dstep$.

		\end{itemize}
		So our hypothesis is not realisable.So our assertion is true. $\Box$\\

@@

		\textbf{Proof}	
		To solve the permutation pattern for a permutation in $\AV_n(213,231)$, 
		we find a find a match of the stripe of the pattern in the stripe of the text.
		This can be done linearly by a greedy algorithm, 
		by matching a step whenever it is possible.
		And thank to the definition of the definition of a stripe in \textbf{Corollary \ref{corollary:stripe}},
		we do not have to compute the stripe advance.
		Therefore we have an linear (online) algorithm.$\Box$\\

@@

			For the algorithm we introduce a decomposition,
			we decompose the motif into
			adjacent element of same step in the stripe 
			(called such sequence segment),
			add the last element to the right most segment,
			and label them form right to left
			with increasing number.
			Let's call this decomposition $S$.
			For each segment, we call important 
			the leftmost element denoted by $IMP$.
			For example, given the motif $(12,11,10,1,2,3,4,9,8,5,6,7)$,
			$S(1)=(5,6,7)$, $IMP(1)=5$, 
			$S(2)=(9,8)$, $IMP(2)=9$, 
			$S(3)=(1,2,3,4)$, $IMP(3)=1$, 
			$S(4)=(12,11,10)$ and $IMP(4)=12$.\\

			Given a ascent (descent) segment $S(s)$,
			if we want to
			match the suffix $s_ns_{s-1}...s_1$
			starting with an ascent (descent),
			and given that we know every
			match of $s_{s-1}...s_1$,
			the optimal way of matching
			$s_{s-1}...s_1$
			is to choose the match
			that minimize (maximize)
			the maximal (minimal)
			element of the match
			and that allow a match
			of $s_n$.			
			In other word if we want to match 
			$\pmotif[IMP(s):]$
			with $\ptext[i:]$
			and match $IMP(s)$
			with $i$.
			The optimal way
			of matching
			$\pmotif[IMP(s-1):]$
			is to choose the
			minimal (maximal) element $\ptext(i')$
			such that :
			(1) $\pmotif[IMP(s-1):]$ is matched with $\ptext[i':]$
			and $IMP(s-1)$ is matched with $e$.
			(2) The segment $S(s)$ is matched with $\ptext[i:i'-1]$
			and $IMP(s)$ is matched with $i$.
			(3) Every elements of the match of (2),
			is inferior (superior) to the minimal (maximal) element of the match of (1).
			Indeed when we will 
			match $s_{n+1}s_ns_{s-1}...s_1$
			more element will be available,
			because every matched 
			element of $s_{n+1}$
			must be superior (inferior)
			to every matched element
			of $s_{s-1}...s_1$.\\

@@

			There exists a match of $\pmotif$ in $\ptext$ if and only if
			there exists a $LM(n,i)$ for $1 \leq i \leq |\ptext|$,
			with $n$ the number of segment in $\pmotif$.
			Moreover the basic case can be computed in $O(|\ptext|^2)$
			and the induction on $O(|\pmotif|*|\ptext|^2)$ $\Box$.

@@

			\textbf{Proof }
			We consider the following problem :\\

@@

			If $|\pmotif| \notin \x$ there exists a match if and only if \\	$\bigcup_{0<k<|\ptext|,0<min<max<|\ptext|}\mathbb{P}_{\pmotif,\ptext,min,max}(0,k)$
			is true. $\Box$

@@

	\textbf{Proof} Let's $s$ is a longest subsequence avoiding (213,231) with last element at index $f$ in $\pi$, 
	suppose that $P(\pi)$ is not a longest increasing subsequence with last element at index $f$. Let's $s_m$ be a longest increasing subsequence with last element $f$.
	Thus $|s_m|>P(\pi)$, clearly the sequence $s_m \cup M(\pi)$
	is avoiding (213,231) and is longer than $s$ witch is not possible. 
	The case for $M(\pi)$ follows the same idea.$\Box$\\

@@

	\textbf{Proof} The proposition \ref{proposition:longestIncreasingSubsequence} lead to algorithm 
	where we have to compute longest increasing and decreasing subsequence ending at every index. Then finding the maximum sum of longest increasing and decreasing subsequence ending at the same index.
	Computing the longest increasing and decreasing can be done in $O(|\ptext|*log(log(|\ptext|)))$ time and $O(n)$ space (see \cite{Bespamyatnikh00enumeratinglongest}), then finding the maximum can be done in linear time.$\Box$\\

@@

	\textbf{Proof } Consider the following problem, 
	that compute the longest stripe common to $\pi_1$ and $\pi_2$.
	Given two permutation $\pi_1$ and $\pi_2$.\\

@@

	For every pair $i,j$ we either ignore the element of $\pi_1$,
	either ignore the element of $\pi_2$, 
	either we match as the same step (if possible).
	Those relation lead to a $O(|\pi_1|^3*|\pi_2|^3)$ time and $O(|\pi_1|^3*|\pi_2|^3)$ space algorithm.$\Box$

>>>>

\begin{corollary}
\label{corollary:minmaxelement}
$\pi \in \AV_n(213,231)$ if and only if for $1 \leq i \leq n$, 
$\pi[i:]$ start either with the maximal element
or the minimal element of $\pi[i:]$.
\end{corollary}

@@

\begin{lemma}
\label{lemma:MatchStripeToPermutation}
Given two permutations $\ptext$,$\pmotif$ avoiding (231,213), If $\stripew{\pmotif}$ is a motif of stripe $\stripew{\ptext}$ by a subsequence $s$, then $\pmotif$ is a motif of $\ptext$ by subsequence $s$.
\end{lemma}

\begin{proof} 
We prove the lemma by induction on the size of the motif. Suppose that we have the motif $(12)$, thus the stripe is $\ustep$. If there is a match in stripe, then there exists two (contiguous) increasing elements in the text, which is a match in permutation. Same goes for the permutation $(21)$. Now, suppose that the lemma is true for every motif of size $n$. Let $\pmotif$ be a motif of size $n+1$ avoiding $(213,231)$, and $\ptext$ a permutation avoiding $(213,231)$. If there is a match of $\stripew{\pmotif}$ in $\stripew{\ptext}$ by subsequence $s$, then there is a match of $\stripew{\pmotif}[2:]$ in $\stripew{\ptext}[2:]$ by subsequence $s[2:]$, and by induction there is a match of $\pmotif[2:]$ in $\ptext[2:]$ by subsequence $s[2:]$. Moreover suppose that the first element the stripe of the motif is ascend (descent), and by lemma \ref{lemma:first element is 1 or n} the minimal (maximal) element, and remark that a subsequence of a permutation avoiding (231,213) is also avoiding (231,213), thus the first element of the subsequence $s$ is either the minimal (maximal) element which complete our proof.
\end{proof}

\begin{proposition}
\label{proposition:patternMatchingStripe}
Let $\ptext$ and $\pmotif$ be two permutations avoiding (213,231).
$\pmotif$ is a motif of $\ptext$ if and only if the 
stripe of $\pmotif$ is a motif of the stripe of $\ptext$.
\end{proposition}

\begin{proof}
$\Rightarrow$ Suppose that $\pmotif$ is a motif of $\ptext$ by subsequence $s$. By definition $s$ normalized is equal to
$\pmotif$ so they have the same stripe.\\ 
$\Leftarrow$ This is proved by lemma \ref{lemma:MatchStripeToPermutation}.
\end{proof}

%We need the following lemmata
%(the proofs of Lemma~\ref{lemma:upup} and Lemma~\ref{lemma:downdown} 
%are analogous and we omit them).
%
%\begin{lemma}
%	\label{lemma:updown}
%	Let $\pi \in \AV_n(213,231)$.
%	For all $1 \leq i < j \leq n$, 
%	if $\stripe{\pi}{i}=\ustep$
%	and $\stripe{\pi}{j}=\dstep$
%	then $\pi[i] < \pi[j]$.
%\end{lemma}
%		
%\begin{proof} 
%By induction on the size of the permutation.
%The proposition is certainly true for the $12$ and $21$.
%Suppose the proposition holds true for $\AV_n(213,231)$.
%Let $\pi \in \AV_{n+1}(213,231)$ and
%$\pi'$ be the permutation $\pi[2:]$.
%$\pi' \in \AV_n(213,231)$.
%By induction hypothesis, we only need to compare the first
%element of $\pi'$ to every element in $\pi'$.
%According to lemma~\ref{lemma:first element is 1 or n},
%the first element of $\pi$ is either $1$ or $n$.
%If the first element of $\pi$ is $1$ then $s_\pi(1) = a$
%and $\pi(i) < \pi(j)$ for every $2 \leq j \leq n$.
%If the first element of $\pi$ is $n$ then
% $s_\pi(1) = d$.
%\qed
%\end{proof}
%
%\begin{lemma}
%	\label{lemma:upup}
%	Let $\pi \in \AV_n(213,231)$.
%	For all $1 \leq i < j \leq n$,
%	if $\stripe{\pi}{i}=\ustep$
%	and $\stripe{\pi}{j}=\ustep$
%	then $\pi[i] < \pi[j]$.
%\end{lemma}
%		
%
%\begin{lemma}
%	\label{lemma:downdown}
%	Let $\pi \in \AV_n(213,231)$.
%	For all $1 \leq i < j \leq n$,
%	if $\stripe{\pi}{i} = \dstep$
%	and $\stripe{\pi}{j} = \dstep$
%	then $\pi[i] > \pi[j]$.
%\end{lemma}
%
%
%Most of the interest of the above lemmata stems from the following proposition.
%
%\begin{proposition}
%	\label{proposition:patternMatchingStripe}
%	Let $\ptext$ and $\pmotif$ be two permutations avoiding (213,231).
%	$\pmotif$ is a motif of $\ptext$ if and only if the 
%	stripe of $\pmotif$ is a motif of the stripe of $\ptext$.
%\end{proposition}
%
%		
%		\textbf{Proof} \\
%		$\Rightarrow$ Suppose that $\pmotif$ is a motif of $\ptext$
%		by subsequence $s$.
%		By definition $s$ normalized is equal to
%		$\pmotif$ so they have the same stripe.\\ 
%		$\Leftarrow$ 
%		Let $\ptext$ be a permutation avoiding $(213,231)$, 
%		$S_1$ be its stripe, 
%		$\pmotif$  be a permutation avoiding $(213,231)$, 
%		and $S_2$ its stripe.
%		Let $\phi$ be the function
%		that match $S_2$ to $S_1$.
%		We define $\varphi$ as, 
%		$\forall x \in [|\pmotif|-1]$,
%		$\varphi(x) = \phi(x)$,
%		and $\varphi(|\pmotif|) = \phi(|\pmotif|-1)+1$
%		Suppose that $\exists x,y \in [|\pmotif|]$, 
%		$\pmotif(x)<\pmotif(y)$ 
%		and $\ptext(\varphi(x))>\ptext(\varphi(y))$,
%		without lost of generality we can suppose that $x<y$,
%		Let see all the case possible that can make this 
%		hypothesis possible :
%		\begin{itemize}		
%			\item if $\pmotif(x)<\pmotif(y)$, 
%			$\stripe{\pmotif}{x}=\ustep$ 
%			and $\stripe{\pmotif}{y}=\ustep$
%			(if x and y are increasing in $\pmotif$),
%			then $\stripe{\ptext}{\varphi(x)} =\ustep$ and $\stripe{\ptext}{\varphi(y)}=\ustep$,
%			(the match are also increasing).
%			As $x<y$ and as $\varphi$ is an increasing function, 
%			$\varphi(x) < \varphi(y)$.
%			And thus, by \textbf{Lemma \ref{lemma:upup}},
%			$\ptext(\varphi(x)) < \ptext(\varphi(y))$ .
%			Which contradict our hypothesis,
%			so this case is not possible.
%		
%			\item if $\pmotif(x)<\pmotif(y)$, 
%			$\stripe{\pmotif}{x}=\ustep$ 
%			and $\stripe{\pmotif}{y}=\dstep$
%			then $\stripe{\ptext}{\varphi(x)}=\ustep$ and $\stripe{\ptext}{\varphi(y)}=\dstep$,
%			As $x<y$ and as $\varphi$ is an increasing function, 
%			$\varphi(x) < \varphi(y)$.
%			And thus, by \textbf{Lemma \ref{lemma:updown}},
%			$\ptext(\varphi(x)) < \ptext(\varphi(y))$ .
%			Which contradict our hypothesis,
%			so this case is not possible.			
%
%			\item if $\pmotif(x)>\pmotif(y)$, 
%			$\stripe{\pmotif}{x}=\dstep$ 
%			and $\stripe{\pmotif}{y}=\dstep$
%			then $\stripe{\ptext}{\varphi(x)}=\dstep$ and $\stripe{\ptext}{\varphi(y)}=\dstep$,
%			As $x<y$ and as $\varphi$ is an increasing function, 
%			$\varphi(y) < \varphi(x)$.
%			And thus, by \textbf{Lemma \ref{lemma:downdown}},
%			$\ptext(\varphi(y)) > \ptext(\varphi(x))$ .
%			Which contradict our hypothesis,
%			so this case is not possible.
%			
%			\item if $\pmotif(x)>\pmotif(y)$, 
%			$\stripe{\pmotif}{x}=\dstep$ 
%			and $\stripe{\pmotif}{y}=\ustep$
%			then $\stripe{\ptext}{\varphi(x)}=\dstep$ and $\stripe{\ptext}{\varphi(y)}=\ustep$,
%			As $x<y$ and as $\varphi$ is an increasing function, 
%			$\varphi(y) < \varphi(x)$.
%			And thus, by \textbf{Lemma \ref{lemma:updown}},
%			$\ptext(\varphi(y)) > \ptext(\varphi(x))$ .
%			Which contradict our hypothesis,
%			so this case is not possible.$\Box$
%			
%			\item If $y = |\pmotif|$ and $x=|\pmotif|-1$,
%			Clearly if $\stripe{\pmotif}{x}=\ustep$,
%			then $\pmotif(y)-\pmotif(x)>0$ 
%			and because we have a match in the ribbon
%			$\ptext(\varphi(y))-\ptext(\varphi(x))>0$.
%			Same idea goes if $\stripe{\pmotif}{x}=\dstep$.
%			So this case is not possible.
%			
%			\item if $y = |\pmotif|$ and $x<|\pmotif|-1$,
%			if $\stripe{\pmotif}{x}=\ustep$ ie
%			$\pmotif(x+1)-\pmotif(x)>0$. Then
%			we must have either
%			$\pmotif(x)<\pmotif(x+1)<\pmotif(|\pmotif|)$
%			or $\pmotif(x)<\pmotif(|\pmotif|)<\pmotif(x+1)$ 
%			to avoid $231$ or $213$ in the motif.
%			Because we have a match in the stripe
%			and what we prove above,
%			$\ptext(\varphi(x+1)-\ptext(\varphi(x))>0$.
%			But by hypothesis $\ptext(\varphi(|\ptext|))<\ptext(\varphi(x))$,
%			so we have either 		
%			$\pmotif(|\pmotif|)<\pmotif(x)<\pmotif(x+1)$
%			or $\pmotif(|\pmotif|)<\pmotif(x)<\pmotif(x+1)$ 
%			which both lead to a $231$ or a $213$ motif
%			in the text which is not possible.
%			The same idea goes if $\stripe{\pmotif}{x}=\dstep$. 			
%			
%		\end{itemize}
%		So our hypothesis is not realisable.So our assertion is true. $\Box$\\

@@

		\begin{proof}
		To solve the permutation pattern for a permutation in $\AV_n(213,231)$, 
		we find a find a match of the stripe of the pattern in the stripe of the text.
		This can be done linearly by a greedy algorithm, 
		by matching a step whenever it is possible.
		And thank to the definition of the definition of a stripe in \textbf{Corollary \ref{corollary:minmaxelement}},
		we do not have to compute the stripe advance.
		Therefore we have an linear (online) algorithm.
		\end{proof}

@@

			For the proof and the algorithm we introduce a decomposition,
			we decompose the motif into
			adjacent element of same step in the stripe 
			(called such sequence segment),
			add the last element to the right most segment,
			and label them form right to left
			with increasing number.
			Let's call this decomposition $S$.
			For each segment, we call important 
			the leftmost element denoted by $IMP$.
			For example, given the motif $(12,11,10,1,2,3,4,9,8,5,6,7)$,
			$S(1)=(5,6,7)$, $IMP(1)=5$, 
			$S(2)=(9,8)$, $IMP(2)=9$, 
			$S(3)=(1,2,3,4)$, $IMP(3)=1$, 
			$S(4)=(12,11,10)$ and $IMP(4)=12$.\\

			\begin{proof}
			Given a ascent (descent) segment $S(s)$,
			if we want to
			match the suffix $s_ns_{s-1}...s_1$
			starting with an ascent (descent),
			and given that we know every
			match of $s_{s-1}...s_1$,
			the optimal way of matching
			$s_{s-1}...s_1$
			is to choose the match
			that minimize (maximize)
			the maximal (minimal)
			element of the match
			and that allow a match
			of $s_n$.			
			In other word if we want to match 
			$\pmotif[IMP(s):]$
			with $\ptext[i:]$
			and match $IMP(s)$
			with $i$.
			The optimal way
			of matching
			$\pmotif[IMP(s-1):]$
			is to choose the
			minimal (maximal) element $\ptext(i')$
			such that :
			(1) $\pmotif[IMP(s-1):]$ is matched with $\ptext[i':]$
			and $IMP(s-1)$ is matched with $e$.
			(2) The segment $S(s)$ is matched with $\ptext[i:i'-1]$
			and $IMP(s)$ is matched with $i$.
			(3) Every elements of the match of (2),
			is inferior (superior) to the minimal (maximal) element of the match of (1).
			Indeed when we will 
			match $s_{n+1}s_ns_{s-1}...s_1$
			more element will be available,
			because every matched 
			element of $s_{n+1}$
			must be superior (inferior)
			to every matched element
			of $s_{s-1}...s_1$.\\

@@

			There exists a match of $\pmotif$ in $\ptext$ if and only if
			there exists a $LM(n,i)$ for $1 \leq i \leq |\ptext|$,
			with $n$ the number of segment in $\pmotif$.
			Moreover the basic case can be computed in $O(|\ptext|^2)$
			and the induction on $O(|\pmotif|*|\ptext|^2)$.
			\end{proof}

@@

			\begin{proof}
			We consider the following problem :\\

@@

			If $|\pmotif| \notin \x$ there exists a match if and only if \\	$\bigcup_{0<k<|\ptext|,0<min<max<|\ptext|}\mathbb{P}_{\pmotif,\ptext,min,max}(0,k)$
			is true.			
			\end{proof}

@@

	\begin{proof}
	Let's $s$ is a longest subsequence avoiding (213,231) with last element at index $f$ in $\pi$, 
	suppose that $P(\pi)$ is not a longest increasing subsequence with last element at index $f$. Let's $s_m$ be a longest increasing subsequence with last element $f$.
	Thus $|s_m|>P(\pi)$, clearly the sequence $s_m \cup M(\pi)$
	is avoiding (213,231) and is longer than $s$ witch is not possible. 
	The case for $M(\pi)$ follows the same idea.
	\end{proof}

@@

	\begin{proof}
	The proposition \ref{proposition:longestIncreasingSubsequence} lead to algorithm 
	where we have to compute longest increasing and decreasing subsequence ending at every index. Then finding the maximum sum of longest increasing and decreasing subsequence ending at the same index.
	Computing the longest increasing and decreasing can be done in $O(|\ptext|*log(log(|\ptext|)))$ time and $O(n)$ space (see \cite{Bespamyatnikh00enumeratinglongest}), then finding the maximum can be done in linear time.
	\end{proof}

@@

	\begin{proof}
	Consider the following problem, 
	that compute the longest stripe common to $\pi_1$ and $\pi_2$.
	Given two permutation $\pi_1$ and $\pi_2$.\\

@@

	For every pair $i,j$ we either ignore the element of $\pi_1$,
	either ignore the element of $\pi_2$, 
	either we match as the same step (if possible).
	Those relation lead to a $O(|\pi_1|^3*|\pi_2|^3)$ time and $O(|\pi_1|^3*|\pi_2|^3)$ space algorithm.		
	\end{proof}
